%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Laura Roldán-Gómez}{}

\position{PhD Candidate}
\address{University of Exeter, UK}

\email{\href{mailto:lr480@exeter.ac.uk}{\nolinkurl{lr480@exeter.ac.uk}}}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {January, 2024}
    {Laura Roldán-Gómez~~~·~~~Curriculum Vitae}
  {\thepage~ of \pageref{LastPage}~}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{PhD Candidate Advanced Quantitative Methods }{University of Exeter}{United Kingdom}{Expected 2024}{}\vspace{-4.0mm}
    \cventry{MRes. Advanced Quantitative Methods}{}{}{2020}{}\vspace{-4.0mm}
    \cventry{MRes. Sustainable Futures}{University of Bristol}{United Kingdom}{2019}{}\vspace{-4.0mm}
    \cventry{MSc. Environmental Management}{Javeriana University}{Colombia}{2014}{}\vspace{-4.0mm}
    \cventry{BSc. Biology}{Los Andes University}{Colombia}{2007}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\begin{cventries}
    \cventry{F.S. Sosa Rodriguez, F. Pineda Campos, A. Flores Diaz, L. Roldan Gomez, E. Rios Patron. (2023). Estrategias para la integración de sujetos y actores sociales en la restauración del ciclo socionatural del agua. En: J.R. Garcia Barrios, S. Mozka Estrada (Eds). Problemas del agua en México. ¿Cómo abordarlos? (pp. 339-361).}{}{}{(2023)}{}\vspace{-4.0mm}
    \cventry{L. Jasny, C. Prell, E. Schiffer, L. Roldan, M. Barnes, P. Matous, M. Hamilton, D. Jacobs, J. Sayles, A. Guerrero. Participant Engagement in Environmentally Focused Social Network Data Collection. Social Networks}{}{}{2021}{}\vspace{-4.0mm}
    \cventry{Ungar, P., Osejo, A., Roldán, L., Buitrago, E. (2014). Caracterización del sistema social asociado al territorio. En: Sarmiento, C. y P. Ungar (Eds). Aportes a la delimitación del páramo mediante la identificación de los límites inferiores del ecosistema (pp. 54-68).}{}{}{2014}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{conference-presentations}{%
\section{Conference Presentations}\label{conference-presentations}}

\begin{cventries}
    \cventry{Sunbelt}{}{}{2023}{}\vspace{-4.0mm}
    \cventry{ECPR - General Conference}{}{}{2022}{}\vspace{-4.0mm}
    \cventry{Sunbelt}{}{}{2022}{}\vspace{-4.0mm}
    \cventry{PolNet}{}{}{2022}{}\vspace{-4.0mm}
    \cventry{European Conference of Social Networks}{}{}{2021}{}\vspace{-4.0mm}
    \cventry{Sunbelt}{}{}{2020}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{teaching-experience}{%
\section{Teaching Experience}\label{teaching-experience}}

\begin{cventries}
    \cventry{Co-lead Introduction to Social Network Analysis and Socio-Ecological Network Analysis}{Universidad Ibero}{México}{2023}{}\vspace{-4.0mm}
    \cventry{Co-lead Statistical Modelling in R}{University of Exeter}{United Kingdom}{2022}{}\vspace{-4.0mm}
    \cventry{Co-lead Introduction to R}{University of Exeter}{United Kingdom}{2022}{}\vspace{-4.0mm}
    \cventry{Introduction to Social Network Analysis with R and statnet
}{Teaching Assistant, Heriot Watt University}{United Kingdom}{Jan 2022}{}\vspace{-4.0mm}
    \cventry{Introduction to Social Network Analysis}{Teaching Assistant, University of Exeter}{United Kingdom}{Jan-Mar 2021}{}\vspace{-4.0mm}
    \cventry{Data Analysis in Social Science I}{}{}{Jan-Mar 2021}{}\vspace{-4.0mm}
    \cventry{Data Analysis in Social Science II}{}{}{Sep-Dec 2020}{}\vspace{-4.0mm}
    \cventry{Institute of Coding Summer School - R and Python}{}{}{Jun-Jul 2020}{}\vspace{-4.0mm}
    \cventry{Workshop on Social Networks}{}{}{Sep 2019}{}\vspace{-4.0mm}
    \cventry{NHS R Training Course}{}{}{May 2019}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{workshops}{%
\section{Workshops}\label{workshops}}

\begin{cventries}
    \cventry{Spatial Social Network Analysis}{Sunbelt}{Portland, Oregon - USA}{2023}{}\vspace{-4.0mm}
    \cventry{Relational Spatial Analysis}{Technische Universität Berlin}{Germany}{2022}{}\vspace{-4.0mm}
    \cventry{Relational Event Models}{Carter Butts at Sunbelt}{Australia}{2022}{}\vspace{-4.0mm}
    \cventry{Social-Ecological Network Analysis}{Centre for Complex Systems Studies, Utrecht University}{Netherlands}{2022}{}\vspace{-4.0mm}
    \cventry{Learning from Geoenvironmental Data: Tools for a Changing Planet}{Venice International University}{Italy}{2022}{}\vspace{-4.0mm}
    \cventry{Advanced Social Network Techniques}{NUSC Summer School in Network and Data Science }{Online}{2021}{}\vspace{-4.0mm}
    \cventry{Introduction to Social and Ecological Network Analysis}{University of Maryland - SESYNC}{USA}{2019}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{employment-history}{%
\section{Employment History}\label{employment-history}}

\begin{cventries}
    \cventry{Contractor}{Unit for Rural and Agricultural Planning}{Colombia}{2017-18}{}\vspace{-4.0mm}
    \cventry{Research Assistant}{University of Exeter - Geography Dept}{United Kingdom}{Mar-Nov 2014}{}\vspace{-4.0mm}
    \cventry{Researcher}{Institute for Research on Biological Resources Alexander von Humboldt}{Colombia}{2011-14}{}\vspace{-4.0mm}
    \cventry{Contractor}{National Natural Parks System}{Colombia}{2007-10}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{other-roles}{%
\section{Other roles}\label{other-roles}}

\begin{cventries}
    \cventry{Panel Moderator}{Tips and Tricks for your PhD}{}{2023}{}\vspace{-4.0mm}
    \cventry{Council Member}{Early and Mid Career Researchers in Social Network Analysis}{}{2022-ongoing}{}\vspace{-4.0mm}
    \cventry{Coordination group member}{Colectivo Riberear, Mexico}{}{2020-ongoing}{}\vspace{-4.0mm}
\end{cventries}


\label{LastPage}~
\end{document}
